D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-05-12 doc/article/article.tex
Draft

\subsubsection{Text Digitization}
Since the task of converting an image of text into the relative string has already been solved in various ways, we settled upon the Microsoft \textit{Trocr Handwritten} Transformer model; more precisely, the \textit{small} version of it. [TODO: Fare esperimenti e provarne altri]. Every bounding box containing text that has been found is later passed to the model, and the resulting string generated by the model is linked to it.\\

@@

Some examples of the different models applied to our graph diagram dataset can be seen in Figure~\ref{fig:text_digitization_results_1}.

@@

>>>>

\subsubsection{Text Digitization}
Since the task of converting an image of text into the relative string has already been solved in various ways, we settled upon the Microsoft \textit{Trocr Handwritten} Transformer model; more precisely, the \textit{base} version of it. Every bounding box containing text that has been found is later passed to the model, and the resulting string generated by the model is linked to it.\\

@@

Some examples of the different models applied to our graph diagram dataset can be seen in Figure~\ref{fig:text_digitization_results_1} and in Figure~\ref{fig:text_digitization_results_2}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{text_digitization_results_2.png}
\caption{Some results in which the \textit{trocr-base-handwritten} fails.}
\label{fig:text_digitization_results_2}
\end{figure}
